\section{Numerical Methods}
This chapter contains an overview of the governing equations used in Star-CCM+ for the modelling of multiphase flows with a focus on
eulerian multiphase (EMP) flow and the volume of fluid (VOF) method. Turbulence and the Shear Stress Transport (SST) k-$\omega$ model is
briefly discussed. The physical processes of evaporation and vaporisation are described.
The ability to model multiple flow regimes, capture interfaces, and the phase interaction closures used in Star-CCM+ are discussed.
The chapter concludes with a description of the numerical methods used in Star-CCM+ along with the apparent limitations~\COMMENT{better word}
of the commercial software in being able to accurately model the problems under consideration.

\subsection{Governing Equations}
\COMMENT{this section is somewhat rough}\hfill\\
Multiphase flow is modelled in Star-CCM+ using various frameworks. The two-fluid - eulerian multiphase - framework solves a set of six equations
to model two-phase flow. A set of transport equations for mass, momentum, and energy are solved for all the phases, which are assumed to
be interpenetrating continua that share a common pressure field. The local instantaneous conservation equations are assumed to be euler averaged and
contain closures based on interfacial terms that define the influences of the phases upon each other.

Although used primarily for modelling dispersed flows, the EMP framework is capable
of resolving both dispersed and separated flow regimes.

The implemented volume of fluid method in Star-CCM+ assumes sufficient mesh resolution
in order to resolve the interface and model separated flows. The interface capturing method solves
the volume fraction transport equation using the High-Resolution Interface Capturing (HRIC) scheme
to maintain a sharp interface between the phases.

Based on the local volume fraction of the phase $i$, $\alpha_{i} = V_{i}/V$, where in each cell $\textstyle\sum\nolimits_{i} \alpha_{i} = 1$.
The material properties in each cell and other flow variables are assumed to be a mixture of the properties of the phases as follows:
\begin{subequations}\label{eq_vof_defs}
\begin{align}
\text{density, } \rho &= \textstyle\sum\nolimits_{i} \alpha_{i} \rho_{i},\\
\text{viscosity, } \mu &= \textstyle\sum\nolimits_{i} \alpha_{i} \mu_{i},\\
\text{velocity, } \vetor{v} &= \textstyle\sum\nolimits_{i} \alpha_{i} \rho_{i} \vetor{v}_{i}/ \rho,\\
\text{specific heat, } C_{p} &= \textstyle\sum\nolimits_{i} \alpha_{i} C_{p,i} \rho_{i}/\rho,\\
\text{thermal conductivity, } k &= \textstyle\sum\nolimits_{i} \alpha_{i} k_{i},\\
\text{enthalpy, } \mathrm{H} &= \textstyle\sum\nolimits_{i} \alpha_{i} \rho_{i} \mathrm{H}_{i}/\rho + |\vetor{v}|^{2}/2.
\end{align}
\end{subequations}

\noindent where $\rho_{i}$ is the density, $\mu_{i}$ is the dynamic viscosity,
$\vetor{v}_{i}$ is the velocity, $C_{p,i}$ is the specific heat, $k$ is the thermal conductivity, and $\mathrm{H}_{i}$ is the enthalpy of the phase $i$.

The diffusion velocity of phase $i$, $\vetor{v}_{d,i}$, is defined as the difference between the velocity of the phase and the mixture
such that \[\vetor{v}_{d,i} = \vetor{v}_{i} - \vetor{v}.\]

A set of volume fraction transport and mass, momentum, and energy conservation equations are solved for each phase.
In cases of two-phase flow, Star-CCM+ solves the volume fraction transport equation only for the first phase.

\subsubsection{Eulerian Multiphase Flow}
The euler averaged mass conservation equation used in the eulerian 
 multiphase formulation is shown in~\ref{eq:emp-mass-conserv}. 
 The right hand side of the equation contains the user defined mass
 source term $\mathrm{S}^{\alpha}_{i}$ and the interfacial mass
 source $\Gamma_k$. The interfacial mass source is the net 
 mass transfer per unit volume from phase $j$ to phase $i$, $m_{ij}$, 
 and from phase $i$ to phase $j$, $m_{ji}$. 
\begin{equation}\label{eq:emp-mass-conserv}
\frac{\partial}{\partial t}
\int\limits_{V} \alpha_{i} \rho_{i} \,\mathrm{d}V
+ \int\limits_{\partial V} \alpha_{i} \rho_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
= \Gamma_{i}
+ \int\limits_{V} \mathrm{S}^{\alpha}_{i} \,\mathrm{d}V.
\end{equation}

\begin{equation}
    \Gamma_{i} = \int\limits_{V} \sum_{j \neq i} (m_{ij} - m_{ji})\,\mathrm{d}V .
\end{equation}
 
%\begin{equation}\label{eq_emp_cont}
%\frac{\partial}{\partial t}\int\limits_{V} \alpha_{i} \rho_{i}\,\mathrm{d}V +
%\int\limits_{\partial V} \alpha_{i} \rho_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
%= \int\limits_{V} \sum_{j \neq i} (m_{ij} - m_{ji})\,\mathrm{d}V + \int\limits_{V} \mathrm{S}^{\alpha}_{i}\,\mathrm{d}V
%\end{equation}
%\begin{itemize}[topsep=0pt, labelindent=40pt,labelsep=5pt, parsep = 2pt, listparindent=2em]
%\item $\vetor{a}$ is the surface area vector,
%\item $\alpha_{i}$ is the volume fraction that fulfills the requirement $\textstyle\sum\nolimits_{i}^{n} \alpha_{i} = 1$,
%\item $\rho_{i}$ is the density,
%\item $\vetor{v}_{i}$ is the velocity,
%\item $m_{ij}, m_{ji}$ is the interphase mass transfer per unit volume from phase $i$ to $j$ and $j$ to $i$ respectively,
%\item $\mathrm{S}^{\alpha}_{i}$ is the user defined mass source term.
%\end{itemize}


The governing momentum conservation equation implemented in the eulerian 
 multiphase formulation is given in~\eq{eq:emp-mom-conserv}. 
 The right hand side of the equation consists the various body and surface forces acting on the 
 fluid volume element. The pressure field, $p$, is assumed to be
 shared by both the phases. The vector $\vetor{g}$ denotes the gravitational acceleration and
 the laminar and turbulent stresses are given by $\tens{T}_{i}$ and $\tens{T}^{t}_{i}$ respectively.
 An additional user defined momentum source term can be appended to the equation using
 $\vetor{S}^{\alpha}_{i}$. Internal forces such as user defined potential forces or 
 solid pressure forces between particles can be accounted for using the $(\vetor{F}_{\text{int}})_{i}$ term.
\begin{equation}\label{eq:emp-mom-conserv}
\begin{split}
\frac{\partial}{\partial t}
\int\limits_{V} \alpha_{i} \rho_{i} \vetor{v}_{i} \,\mathrm{d}V
+ \int\limits_{\partial V} \alpha_{i} \rho_{i} \vetor{v}_{i} \otimes \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
&= -\int\limits_{V} \alpha_{i} \nabla p \,\mathrm{d}V
+ \int\limits_{V} \alpha_{i} \rho_{i} \vetor{g} \,\mathrm{d}V 
+ \int\limits_{\partial V} \left[ \alpha_{i} \left( \tens{T}_{i} + \tens{T}^{t}_{i} \right) \right] \cdot \mathrm{d}\vetor{a} \\
&\quad {} + \int\limits_{V} \left( \vetor{F}_{\text{int}} \right)_{i} \,\mathrm{d}V
+ \int\limits_{V} \vetor{S}^{\alpha}_{i} \,\mathrm{d}V
+ \mathrm{MomTerm}.
\end{split}
\end{equation}

The term $\Gamma$ groups the interphase, interfacial momentum transfer
 terms together
The interphase and interfacial momentum transfer is accounted through
\begin{equation}
    MomTerm =  \int\limits_{V} \vetor{M}_{i}\,\mathrm{d}V 
    + \int\limits_{V} \sum_{j \neq i} (m_{ij}\vetor{v}_{j} - m_{ji}\vetor{v}_{i})\,\mathrm{d}V
\end{equation}
The momentum transfer, that satisfies the equation $\displaystyle \sum\nolimits_{i}\vetor{M}_{i} = 0$,
 contains contributions from the drag, lift, virtual mass, turbulent dispersion, and wall lubrication force
 respectively. These forces are defined as force per cell volume and it follows that
 $\vetor{F}_{ij} = -\vetor{F}_{ji}$.
 \begin{equation}
    \vetor{M}_{i} = \sum_{j \neq i} \left(\vetor{F}_{ij}^{\mathrm{D}}
    + \vetor{F}_{ij}^{\mathrm{L}} + \vetor{F}_{ij}^{\mathrm{VM}} 
   + \vetor{F}_{ij}^{\mathrm{TD}} + \vetor{F}_{ij}^{\mathrm{WL}}\right).
 \end{equation}
%\begin{equation}\label{eq:emp-mom-conserv}
%\begin{split}
%\frac{\partial}{\partial t}\int\limits_{V} \alpha_{i} \rho_{i} \vetor{v}_{i}\,\mathrm{d}V +
%\int\limits_{\partial V} \alpha_{i} \rho_{i} \vetor{v}_{i} \otimes \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
%&= -\int\limits_{V} \alpha_{i} \nabla p\,\mathrm{d}V + \int\limits_{V} \alpha_{i} \rho_{i} \vetor{g}\,\mathrm{d}V
%+ \int\limits_{\partial V}\left[\alpha_{i} \left(\tens{T}_{i} + \tens{T}^{t}_{i}\right)\right]\cdot \mathrm{d}\vetor{a}\\
%&\,\,{} + \int\limits_{V} \vetor{M}_{i}\,\mathrm{d}V 
%+ \int\limits_{V}\left(\vetor{F}_{\text{int}}\right)_{i}\,\mathrm{d}V
%+ \int\limits_{V}\vetor{S}^{\alpha}_{i}\,\mathrm{d}V 
%+ \int\limits_{V} \sum_{j \neq i} (m_{ij}\vetor{v}_{j} - m_{ji}\vetor{v}_{i})\,\mathrm{d}V
%%\end{equation}
%where for the phase $i$
%\begin{itemize}[topsep=0pt, labelindent=40pt,labelsep=5pt, parsep = 2pt, listparindent=2em]
%\item $p$ is the pressure,
%\item $\vetor{g}$ is the gravitational force vector,
%\item $\tens{T}_{i}, \tens{T}^{t}_{i}$ are the molecular and turbulent stresses respectively,
%\item $\vetor{M}_{i}$ is the interphase momentum transfer term per unit volume that satisfies $\textstyle\sum\nolimits_{i = 1}^{n}\vetor{M}_{i} = 0$,
%\item $\left(\vetor{F}_{\text{int}}\right)_{i}$ is the internal force vector that consists of either the
%solid pressure force between particles or user defined potential force,
%\item $\vetor{S}^{\alpha}_{i}$ is the user defined momentum source term.
%\end{itemize}
The conservation of energy as solved in the eulerian multiphase formulation is shown in~\ref{eq:emp-en-conserv}
 Although written here for total energy of the phase, $E_{i}$, the equation can be either solved for the total
 enthalpy, $H_{i}$, or the temperature $T_{i}$. 
\begin{align}\label{eq:emp-en-conserv}
\frac{\partial}{\partial t}
\int\limits_{V} \alpha_{i} \rho_{i} E_{i} \,\mathrm{d}V
+ \int\limits_{\partial V} \alpha_{i} \rho_{i} 
[ 
    \underbrace{
        h_{i}^{\text{REF}} 
+ \int\limits_{T_{i}^{\text{REF}}}^{T_{i}} C_{p,i}(T') \,\mathrm{d}T' 
+ \frac{1}{2} \vetor{v}_{i} \cdot \vetor{v}_{i}
}_{\text{total enthalpy, $H_{i}$}}
]&
\vetor{v}_{i} \cdot \mathrm{d}\vetor{a} 
= \int\limits_{\partial V} \alpha_{i} (k_{\mathrm{eff}})_{i} \nabla T_{i} \cdot \mathrm{d}\vetor{a}
+ \int\limits_{\partial V} \tens{T}_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}\nonumber \\
& + \int\limits_{V} \vetor{f_{b}}_{i} \cdot \vetor{v}_{i} \,\mathrm{d}V
+ \int\limits_{V} \mathrm{S}_{u,i} \,\mathrm{d}V + EnTerm.
\end{align}
The total energy can be related to the total enthalpy of the phase using  $\mathrm{E}_{i} = \mathrm{H}_{i} - p/\rho_{i}$.
The right hand side of the equation consists of the viscous stress tensor $\tens{T}_{i}$,
 the body force vetor $\vetor{f{b}}_{i}$, and the effective thermal conductivity $(k_{\mathrm{eff}})_{i}$.
 The effective thermal conductivity of the phase $i$ is defined using laminar and turbulent 
 contributions as \[(k_{\mathrm{eff}})_{i} = k_{i} + \frac{\mu_{t,i} C_{p,i}}{\sigma_{t,i}},\]
 where $k_{i}$ is the thermal conductivity, $\mu_{t,i}$ the turbulent viscosity,
 $C_{p,i}$ the specific heat, and $\sigma_{t,i}$ the turbulent thermal diffusion Prandtl number of the phase.

 Along with a user-defined energy source term $\mathrm{S}_{u,i}$,
 the equation contains the interfacial and interphase energy terms that are gathered together
 and denoted using $EnTerm$.
 \begin{equation}
    EnTerm = \int\limits_{V} \sum_{j \neq i} Q_{ij}\,\mathrm{d}V +
 \int\limits_{V} \sum_{ij} Q_{i}^{(ij)}\,\mathrm{d}V 
 + \int\limits_{V} \sum_{j \neq i} (m_{ij} - m_{ji})h_{i}(T_{ij})\,\mathrm{d}V
 \end{equation}
$Q_{ij}$ is the heat transfer from phase $i$ to phase $j$ due to temperature difference between the phases,
$Q_{i}^{(ij)}$ is the heat transfer between the phase $i$ and the interface which accounts for phenomenon
such as evaporation and boiling,
$h_{i}(T_{ij})$ is the enthalpy of the phase $i$ evaluated at the temperature $T_{ij}$ of the interface.
The interphase energy terms are related as follows:
\begin{itemize}
\item for cases where heat is exchanged only through thermal diffusion, the interphase heat transfer rates satisfy $Q_{ij} = -Q_{ji}$
\item for cases where heat and mass are transferred only through phase change, the interphase heat and mass transfer rates satisfy
$Q_{i}^{(ij)} + Q_{j}^{(ij)} + \left(m_{ij} - m_{ji}\right)\left(h_{j}(T_{ij}) - h_{i}(T_{ij})\right) = 0$.
\end{itemize}

%The \textbf{energy conservation} equation solved for the phase $i$ is
%\begin{equation}\label{eq_emp_energy}
%\begin{split}
%\frac{\partial}{\partial t}\int\limits_{V} \alpha_{i} \rho_{i} \mathrm{E}_{i}\,\mathrm{d}V +
%\int\limits_{\partial V} \alpha_{i} \rho_{i} \mathrm{H}_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a} &=
%\int\limits_{\partial V} \alpha_{i} (k_{\mathrm{eff}})_{i} \nabla T_{i} \cdot \mathrm{d}\vetor{a} + \int\limits_{\partial V} \tens{T}_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
%+ \int\limits_{V} \vetor{f}_{i} \cdot \vetor{v}_{i}\,\mathrm{d}V +\int\limits_{V}\mathrm{S}_{u,i}\,\mathrm{d}V \\
%&{} + \int\limits_{V} \sum_{j \neq i} Q_{ij}\,\mathrm{d}V +
%\int\limits_{V} \sum_{ij} Q_{i}^{(ij)}\,\mathrm{d}V 
%+ \int\limits_{V} \sum_{j \neq i} (m_{ij} - m_{ji})h_{i}(T_{ij})\,\mathrm{d}V
%\end{split}
%\end{equation}

%\noindent where for the phase $i$,
%\begin{itemize}[topsep=0pt, labelindent=40pt,labelsep=5pt, parsep = 2pt, listparindent=2em]
%\item $\mathrm{E}_{i}$ is the total energy,
%\item $\mathrm{H}_{i}$ is the total enthalpy,
%\item $\tens{T}_{i}$ is the viscous stress tensor,
%\item $T_{i}$ is the temperature,
%\item $\vetor{f}_{i}$ is the body force vector,
%\item $(k_{\mathrm{eff}})_{i}$ is the effective thermal conductivity,
%\item $\mathrm{S}_{u,i}$ is the user defined energy source term,
%\item $Q_{ij}$ is the heat transfer from phase $i$ to phase $j$ due to temperature difference between the phases,
%\item $Q_{i}^{(ij)}$ is the heat transfer between the phase $i$ and the interface which accounts for phenomenon
%such as evaporation and boiling,
%\item $h_{i}(T_{ij})$ is the enthalpy of the phase $i$ evaluated at the temperature $T_{ij}$ of the interface.
%\end{itemize}

%The effective thermal conductivity of the phase $i$ is defined using the thermal conductivity, $k_{i}$,
%the turbulent viscosity, $\mu_{t,i}$, the specific heat, $C_{p,i}$, and the turbulent thermal diffusion Prandtl number,
%$\sigma_{t,i}$ as \[(k_{\mathrm{eff}})_{i} = k_{i} + \frac{\mu_{t,i} C_{p,i}}{\sigma_{t,i}}\].

%The total enthalpy of the phase $i$, $\mathrm{H}_{i}$, is defined using the specific enthalpy $h_{i}$
%and the kinetic energy as \[\mathrm{H}_{i} = h_{i} + \frac{1}{2}\vetor{v}_{i}\cdot\vetor{v}_{i},\]

%%where the specific enthalpy is further defined using the specific heat of the phase and the reference temperatures
%and heat of formation such that

%\[h_{i} = h_{i}^{\text{REF}} + \int\limits_{T_{i}^{\text{REF}}}^{T_{i}} C_{p,i} (T')\,\mathrm{d}T'.\]

%The total energy of the phase $i$ is then related to the total enthalpy as $\mathrm{E}_{i} = \mathrm{H}_{i} - p/\rho_{i}$.

%The interphase energy terms are related as follows:

%\begin{itemize}
%\item for cases where heat is exchanged only through thermal diffusion, the interphase heat transfer rates satisfy $Q_{ij} = -Q_{ji}$
%\item for cases where heat and mass are transferred only through phase change, the interphase heat and mass transfer rates satisfy
%$Q_{i}^{(ij)} + Q_{j}^{(ij)} + \left(m_{ij} - m_{ji}\right)\left(h_{j}(T_{ij}) - h_{i}(T_{ij})\right) = 0$.
%\end{itemize}
\subsubsection{Volume of Fluid Method}
The distribution of the phase $i$ is driven by the volume fraction transport.
\begin{equation}\label{eq_vof_transport}
\frac{\partial}{\partial t}\int\limits_{V} \alpha_{i}\,\mathrm{d}V +
\int\limits_{\partial V} \alpha_{i} \vetor{v}_{i} \cdot \mathrm{d}\vetor{a}
= \int\limits_{V}\left(\mathrm{S}^{\alpha}_{i} - \frac{\alpha_{i}}{\rho_{i}} \frac{D \rho_{i}}{D t}\right)\,\mathrm{d}V
- \int\limits_{V} \frac{1}{\rho_{i}}\nabla (\alpha_{i}\rho_{i}\vetor{v}_{d,i})\,\mathrm{d}V
\end{equation}
\noindent where $\vetor{a}$ is the surface area vector, $\vetor{v}$ is the mixture velocity, $\vetor{v}_{d,i}$ is the slip velocity, and
$\mathrm{S}^{\alpha}_{i}$ is the user defined phase source term for the phase $i$.


The \textbf{mass conservation} equation solved is
\begin{equation}\label{eq_vof_mass}
\frac{\partial}{\partial t}\int\limits_{V} \rho\,\mathrm{d}V +
\int\limits_{\partial V} \rho \vetor{v} \cdot \mathrm{d}\vetor{a}
= \int\limits_{V} \sum_{i}\mathrm{S}^{\alpha}_{i} \rho_{i}\,\mathrm{d}V
\end{equation}


The \textbf{momentum conservation} equation solved is
\begin{equation}\label{eq_vof_mom}
\begin{split}
\frac{\partial}{\partial t}\int\limits_{V} \rho \vetor{v}\,\mathrm{d}V +
\int\limits_{\partial V} \rho\vetor{v} \otimes \vetor{v} \cdot \mathrm{d}\vetor{a}
&= -\int\limits_{V} \nabla p\,\mathrm{d}V + \int\limits_{V} \rho \vetor{g}\,\mathrm{d}V
+ \int\limits_{\partial V}\left[\left(\tens{T} + \tens{T}^{T}\right)\right]\cdot \mathrm{d}\vetor{a} 
 + \int\limits_{V} \vetor{f}_{b}\,\mathrm{d}V\\
& - \sum_{i}\int\limits_{\partial V} \alpha_{i} \rho_{i} \vetor{v}_{d,i} \otimes \vetor{v}_{d,i} \cdot \mathrm{d}\vetor{a}
 + \int\limits_{V}\vetor{S}^{\alpha}_{i}\,\mathrm{d}V
\end{split}
\end{equation}

\noindent where
\begin{itemize}[topsep=0pt, labelindent=40pt,labelsep=5pt, parsep = 2pt, listparindent=2em]
\item $p$ is the pressure,
\item $\vetor{g}$ is the gravitational force vector,
\item $\tens{T}$ is the viscous stress tensor,
\item $\vetor{f}_{b}$ is the body force vector,
\item $\vetor{S}^{\alpha}_{i}$ is the user defined phase momentum source term.
\end{itemize}


The \textbf{energy conservation} equation solved is
\begin{equation}\label{eq_vof_energy}
\begin{split}
\frac{\partial}{\partial t}\int\limits_{V}\rho \mathrm{E}\,\mathrm{d}V +
\int\limits_{\partial V} \left[\rho \mathrm{H} \vetor{v} + \sum_{i}\alpha_{i} \rho_{i} \mathrm{H}_{i} \vetor{v}_{d,i}\right] \cdot \mathrm{d}\vetor{a}
&= - \int\limits_{\partial V} \vetor{\dot{q}''}  \cdot \mathrm{d}\vetor{a} + \int\limits_{\partial V} \tens{T}\cdot\vetor{v}\,\mathrm{d}\vetor{a}
 + \int\limits_{V}\vetor{f}_{b}\cdot\vetor{v}\,\mathrm{d}V\\
&\qquad{} + \int\limits_{V} \mathrm{S}_{\mathrm{E}}\,\mathrm{d}V
\end{split}
\end{equation}

\noindent where
\begin{itemize}[topsep=0pt, labelindent=40pt,labelsep=5pt, parsep = 2pt, listparindent=2em]
\item $\mathrm{E}$ is the total energy,
\item $\mathrm{H}$ is the total enthalpy,
\item $\vetor{\dot{q}''}$ is the heat flux vector,
\item $\tens{T}$ is the viscous stress tensor,
\item $\mathrm{S}_{\mathrm{E}}$ is the user defined energy source term.
\end{itemize}
\subsection{Modelling Turbulence}
Flows are generally turbulent. Turbulence is chracterised by irregular fluid motion dominated by
 eddies and vortices across a wide range of spatial and temporal scales. The largest eddies
 extract kinetic energy from the mean flow, which is then, through a cascade, transferred
 to the eddies at
 the smallest scale where the energy is dissipated due to viscosity, raising the 
 internal energy of the fluid~\cite{gilmanDevelopmentGeneralPurpose2014, davidsonIntroductionTurbulenceModels}.

RANS models result from decomposing flow variables into
 mean and fluctuating components, $\displaystyle \phi = \overline{\phi} + \phi'$, applying Reynolds averaging,
 which filters out turbulent fluctuations below the
 averaging scale~\cite{besnardTurbulenceMultiphaseFlow1988a, hirschNumericalComputationInternal2007}.
 This operation yields additional Reynolds stress terms representing
 momentum transport by turbulence, which require closure.
 In order to draw closure relations, eddy-viscosity models of turbulence assume that:
 \begin{itemize}
    \item the turbulent scalar flux vector aligns with the mean scalar gradient.
    \item the Reynolds stress tensor is proportional to the mean velocity strain rate through an eddy viscosity.
 \end{itemize}
 While these assumptions simplify modelling, they tend to be, more often than not, invalid
 as they do not fully capture turbulence physics, especiialy in anisotropic 
 or non-equilibrium flow~\cite{popeTurbulentFlows2015}. This limitation can be significant
 in regions with complex strain rates or strong secondary flows.

Although turbulence can be modelled in various ways to various levels of resolutions,
 turbulence in this study has been modelled using the Shear Stress Transport (SST) k-w model.
 The SST k-w model is a two-equation eddy-viscosity turbulence model
 based on the Reynolds-Averaged Navier-Stokes (RANS) equations.
 The model combines the advantages of the $k$-$\omega$ model near walls—which
 accurately resolves boundary layer behaviour—and the $k$-$\varepsilon$ model in
 the free stream, enhancing robustness and accuracy in separated flows~\cite{wilcoxTurbulenceModelingCFD2006}.
 The SST approach uses a blending function to smoothly transition between these models,
 which is especially effective in flows with strong adverse pressure gradients and separation,
 such as multiphase cavity flows~\cite{Menter1994}. Another blending function limits the eddy viscosity 
 in wake regions and a cross-diffusion term ensures consistency between the $k$-$\omega$ and $k$-$\epsilon$
 models.

Since the form of the RANS governing equations remains similar to the governing equations described in the
 previous section, they are not explicity written here but can be found in the Star-CCM+ documentation~\citelater{starccm}.
 The additional equations accounting for the transport of the turbulent kinetic energy and dissipation rate 
 is given in~\ref{eq:turbs-kw}
 \begin{subequations}\label{eq:turbs-kw}
 \begin{align}
    \frac{\partial \rho k}{\partial t}  + \nabla (\rho k \vetor{\overline{v}}) &= \nabla \left[(\mu + \sigma_{k} \mu_{t})\nabla k\right] + P_k
        - \rho \beta^{*}f_{\beta^{*}} (\omega k - \omega_0 k_0) + S_k,\\
    \frac{\partial \rho \omega} + \nabla (\rho \omega \vetor{\overline{v}}) & = \nabla\left[(\mu + \sigma_{\omega}\mu_t) \nabla \omega\right] + P_{\omega}
        - \rho \beta f_{\beta}(\omega^{2} - \omega_{0}^{2}) + S_{\omega},
 \end{align} 
 \end{subequations}
 The turbulent viscosity, $\mu_t$, is calculated as $\mu_{t} = \rho k T{t}$, where $T_{t}$ is the turbulent time scale. 
 where $\sigma_{k}$ and $\sigma_{\omega}$ are the Prandtl numbers for $k$ and $\omega$ respectively. 


The implementation of th model in Star-CCM+ can be further controlled to
 adjust the realisability. Realisability is the postive semi-definiteness of the 
 reynolds stress tensor. The specification of turbulence is done using
 the turbulence intensity and the length scale. The inherent anisotropy 
 in turbulence is accounted for with quadratic and cubic constitutive options
 in the modelling of reynolds stresses. The parameters in the model
 are left on their default values as they are empirically modelled.

\subsection{Evaporation}
The evaporation process is distinguished between occuring at saturation temperatures or not. 
 Evaporation at saturation temperatures, known as vaporisation, is a much faster 
 process in comparison to evaporation at normal~\cite{wickertSimulation}. 
 In case of vaporisation along a heated wall, most CFD models of
 vaporisation treat the energy transfer by partitioning
 the heat flux at the wall into the latent heat of the bubble vaporisation process and the 
 sensible heat transferred to the liquid through conduction, convection, and quencing processes.
 This is determined by the area fractions covered by the liquid and vapour. Correlations between the
 heat flux and wall superheat~\COMMENT{what is superheat} have been made using empirical
 results or based on modelling of sub-processes.

The sub-processes that are primarily taken into account in such determinations are:
\begin{itemize}
    \item number density of nucleation sites
    \item diameter of bubble at time of detachment from the surface
    \item frequency of bubble detachment
\end{itemize}
Nucleation affects the number and distribution of bubbles in the fluid. Walls, particularly so in case they're heated, are more suspectible to be nucleation sites for bubble growth
 as the activation energy for bubble growth is much lower. This nucleation can be modelled through the domain as homogenous or heterogenous - where nucleation sites are modelled using a 
 presumed PDF function or be determined by empirical correlations.~\cite{liaoComputationalModellingFlash2017}

After a stable bubble nucleus has been formed, the growth of the bubble becomes pertinent in the evaluation
 of the diameter at departure and the interphase energy and mass transfer. In the case of an ideal
 spherical bubble undergoing expansion in a uniformly superheated liquid, the rate of growth
 is determined by the surface tension, liquid inertia, and the differnce in pressures inside
 and outside the bubble. Surface tension dominates and restricts the initial bubble growth.
 This initial rapid expansion of the bubble results in the formation of a thin liquid layer separating
 the vapour from the wall surface. This microlayer can be a significant contributor to the 
 bubble growth and heat transfer process.
 As the radius increases and the liquid layer around the bubble cools due to evaporation,
 a decrease in vapour pressure in seen. The dynamics are controlled by thermal diffusion
 and inertia. Inertial effects, however, become less relevant as the bubble growth rate decreases
 and the bubble radius grows. The interphase energy exchange determines further bubble growth.~\cite{sherFlashboilingAtomization2008}

\subsubsection{Effects of low pressure and gravity conditions}
The absence of significant gravitaional forces alters the dynamics of vaporisation - affecting natural convection, buoyancy
 driven phenomenon, and bubble dynamics. Under terrestrial gravity, convection currents develop under thermal
 gradients, thus bringing cooler liquid to the heated surface as the vapour bubble rises due
 to buyoancy. This density driven natural convection is affected in low gravity conditions, maintaining
 the thermal gradient. Bulk fluid movement is affected and heat and mass transfer processes shift
 from being convection dominated to being diffusion dominated.~\cite{cochranEffectsFluidProperties, leeExperimentalComputationalInvestigation2022}

Under low gravity conditions, vapour bubbles tend to remain near the heat source, growing
 signifcantly larger and coalescing with smaller bubbles. Prolonged bubble presence on the
 surface results in drying out of the surface and unsteady rise in surface temperatures.\cite{qiuSingleBubbleDynamicsPool2002}~\COMMENT{Mention some numbers}
 In conditions where the dominance of surface tension forces becomes more pronounced,
 the surfae tension gradients can induce fluid circulation. This is known as Marangoni
 convection and is observed to affect bubble growth and heat transfer.~\cite{xuNumericalStudyMarangoni2014}

Reduced system pressure impacts the overall intensity of heat transfer. The onset of nucleate boiling also
 requires higher superheat values in low pressure conditions.
 Decrease in pressure leads to a lower number of active nucleation sites and increases
 microlayer thickness found at the bubble-wall interface. The local heat flux density from
 microlayer evaporation is impacted and the microlayer evaporation area and depletion time is
 increased. The system is also susceptible to the formation of a continuous vapour film at the 
 surface due to coalescing bubbles unable to escape the surface, reducing the overall heat transfer.~\cite{serdyukovInfluencePressureLocal2023}
 
The affected heat transfer and bubble growth phenomenon further result in lower critical heat fluxes
 and heat transfer efficiency.~\cite{zhangExperimentalTheoreticalStudy2002, PDFMethodAssessing}

\subsubsection{Vaporisation in a superheated liquid}
\COMMENT{------------UNDER CONSTRUCTION--------------------}\hfill\\
Flash evaporation is the intense vaporisation triggered through depressurisation of superheated fluids.

\subsection{Flow Regimes and Closures}
Additional constitutive relations are required to 'close' the set of equations being solved
 that compensate for the various scales blended out due to the averaging procedures.
 Along with the equations of state that govern the physical properties of the materials involved,
 closure relations are required to account for the various interfacial momentum or energy transfer
 mechanisms which are dependent on the interfacial topology.
 The distribution of the phases cannot be accurately estimated
 a priori~\cite{yadigarogluNatureMultiphaseFlows2018} but the macroscopic 
 behaviour of the system is dependent on these small-scale interactions of the 
 phases~\cite{hanrattyPhysicsGasLiquid}. The existence of deformable interfaces 
 leads to more complications.

The various flow regimes in two-phase gas-liquid flows cover the dispersed 
 regimes to the presence of free surfaces. Some simplification is possible by grouping 
 the various interfacial distributions together. Through the perspective of 
 vertical tubes, this ranges from bubbly flows - 
 where gas small gas bubbles are dispersed through the liquid- to annular 
 flows - where the gas in the middle of the cross section 
 and the liquid film at the walls are separated by a free surface.~\cite{yadigarogluNatureMultiphaseFlows2018}
 Star-CCM+ in its implementation of the eulerian-multiphase framework utilises a similar
 dynamic flow regime topology based on the local volume fractions
 of the interacting phases. Based on the increasing volume fraction of the
 secondary phase, $\alpha_{s}$, in a finite volume cell,
 the topology transitions through three principal 
 regimes~\cite{gadaLargeScaleInterface2017}~\citelater{starccm}, where the secondary phase is:
 \begin{itemize}
    \item dispersed in the primary phase (first dispersed regime, $0 \le \alpha_{s} \le \alpha_{fr} $)
    \item separated from the primary phase through a large scale interface (interfacial flow regime, $\alpha_{fr} \le \alpha_{s} \le \alpha_{sr} $) 
    \item continuous while having the primary phase dispersed (second dispersed regime, $\alpha_{sr} \le \alpha_{s} \le 1 $)
 \end{itemize}
The first and second regime terminuses, $\alpha_{fr}$ and $\alpha_{sr}$, mark the values of $\alpha_{s}$
that defines the end of the first dispersed and large scale interface regimes respectively. In the case 
 of EMP, Star-CCM+ uses a regime-specific closure model for 
 the interfacial momentum and energy terms. These models are blended using a weighting
 scheme according to the calculated proportion of each regime in the cell.
 The transport of the volume fraction is done through HRIC, ADIS, or normal 1st or 2nd order convection.

"neither of the two methodology - VOF or two-fluid - is suitable for multiscale flows~\cite{gadaLargeScaleInterface2017}".
"most data for the semi-empirical relations covers rather narrow domains~\cite{yadigarogluNatureMultiphaseFlows2018}"
"if one considers a non flow situation in the two horizontal layers, the forces acting on the 
two fluids and their interface are gravity and surface tension - in this case we speaf of
the RT instability~\cite{hewittModellingStrategiesTwoPhase2018}."
"there exists a wide spectrum of scales, ranging from the global one dictated by the flow
configuration, to the smalles one where turbulent energy is dissipated into heat\cite{shyyComputationalTechniquesComplex1997}"

%While there are multiple numerical methods to account for volume fraction transport, the 
% High-Resolution Interface Capturing scheme is specifically implemented to handle 
% sharp phase interfaces. Free-surface flows with sharp 
% interfaces present a discontinuity
% in the solution domain, causing discretisation errors. This can lead to
% spurious or parasitic currents.~\cite{MIRJALILI2019221}
% Although often negligible, these currents can be accommodated for through 
% the incorporation of an artificial viscosity term.   

%At large scale interfaces, the near-interface flow often exhibits
% laminar characteristics with the development of boundary layers. However, in situations
% with significant velocity gradients, turbulent fluctuations can arise in the
% regions adjacent to the interface (especially when the interface is mobile or
% highly distorted). Recognizing that standard RANS turbulence
% models tend to overpredict turbulence intensity near phase boundaries,
% STAR-CCM+ allows the user to apply turbulence damping strategies
% (e.g., vorticity limiters) which suppress excessive eddy viscosity and
% restore physically consistent laminar sublayers adjacent to the interface.
\subsection{Closures}
Closures are critical to the accurate prediction of the relevant flow variables and the distribution
 of volume fraction~\cite{sugrueRobustMomentumClosure}. Existing literature reviews 
 the overwhelming number of closures available that yield a range of varyinh performance 
 along with their comparison with experimental data, however literature
 presenting CFD simulations tend to choose 'result-oriented' closures that aren't
 transferable to a wider range of flow situations~\cite{krepperValidationClosureModel2018, sugrueAssessmentSimplifiedSet2017}.
 Literature admits that the industry relies on the tunable parameters in the closures to 
 match the specific experimental data being simulated or the arbitrariness of this choice
 to get improved flow predictions~\citelater{[20] rzehak, kriebitzsch; silva [21] (sugrue)}.
 
Models may also provide satisfying predictions for certain parameters or situations while
 failing in others and a general inconsenus prevails while discussing the effects of interfacial
 forces. Early work has tended to neglect 
 the effects of lift or virtual mass forces, or chosen to use constant coefficients to 
 describe them while using formulations for the drag forces based on 
 relevant non-dimensional numbers.~\cite{liaoEulerianModellingTurbulent2018}
 The effect of non-drag forces, however, tends to be as significant on the 
 distribution of phases.~\citelater{liao2014-flashboiling}
 Since it is 
 difficult to separate the effects of the various forces in actual experiments,
 the development of these closures assumes certain idealisations when they're not
 partly or wholly based on empirical data, rendering them highly flow 
 dependent~\citelater{troshko and hassan, [15] in Sugrue}. The authors 
 of~\citelater{troshko and hassan} critiques the methodology of resolving a 
 complex interfacial momentum transfer through a linear superposition 
 of several simple forces as the basis of the discrepancy.
 
The industry has, however, attempted to establish generality that can be transferred 
 to multiple flow situations and has proposed baseline frameworks. There is a general consensus
 that the role of turbulence is underestimated~\cite{colomboBenchmarkingCFDModelling};
 current models also aim to reduce 
 uncertainty and inconsistency in model selection~\cite{colomboBenchmarkingCFDModelling}, 
 adopt closures that avoid "case-specific adjustments to unphysical coefficients and 
 tunable parameters"~\cite{sugrueRobustMomentumClosure}, and utilise more
 physics based closures that are more physically consistent~\cite{liaoEulerianModellingTurbulent2018,colomboBenchmarkingCFDModelling}.

Drag force is generally more dominant than other forces as they tend to be a magnitude
 higher than other forces~\cite{tas-koehlerCriticalAnalysisDrag2021a}. Most drag models perform 
 equally well at low gas volume fractions. However as they are based on ideal conditions, 
 they do not account for bubble swarm effects at higher gas volume fractions and show reduced 
 accuracy. Certain swarm corrections do exist, but they are averaged along a radial profile when
 the swarm effects are also felt in the bulk.~\cite{sugrueRobustMomentumClosure, sugrueAssessmentSimplifiedSet2017,colomboBenchmarkingCFDModelling}
 ~\COMMENT{is there any other update to corrections?}
 The accurate modelling of interaction area density and length becomes relevant for the calculation
 of the drag force. 
 Using the linearised drag coefficient, $A_{D}$, and the relative velocity between the phases
 $\vetor{v}_{r} = \vetor{v}_{j} - \vetor{v}_{i}$, Star-CCM+ implements the drag force as,
 \begin{equation}
    \vetor{F}_{ij}^{D} = A_{D}\vetor{v}_{r}
 \end{equation}
 The linearised drag coefficient is related to the standard definitions of the drag 
 coefficient $C_{D}$ using
 \begin{equation}
    A_{D} = C_{D} \frac{1}{2} \rho_{c} |\vetor{v}_{r}| \frac{a_{cd}}{4}
 \end{equation}
 where $a_{cd}$ is the interfacial area density and $a_{cd}/4$ represents the projected area of
 the equivalent spherical particle. 

The lift force models are particularly sensitive and uncertain in their performance~\cite{sugrueAssessmentSimplifiedSet2017}.
 They suffer from the same discrepancy between performance in low and 
 high gas volume fractions. Moreover, existing 
 lift force implementations in Star-CCM+ fail to replicate the experimental data
 they were derived from.~\cite{sugrueRobustMomentumClosure}
 Assuming $\alpha_{p}$ is the volume fraction of the primary (continuous)
 phase, Star-CCM+ implements the lift force as
 \begin{equation}
    F_{ij}^{L} = C_{L,\text{eff}} \alpha_{d} \rho_{p} 
    \left[\vetor{v}_{r} \times \left(\nabla \times \vetor{v}_{p}\right)\right].
 \end{equation} 

A turbulent dispersion force is supposed to act on the gas phase and 
 spreads this dispersed phase due to turbulence
 in the continuous phase. This is typically modelled as 
 as a diffusion term proportional to the turbulent 
 kinetic energy gradients~\cite{liaoFlashingEvaporationDifferent2013}. 
 The force is theorised to arise from the averaging of the fluctuations
 of the bubbles due to the turbulence.
 \begin{equation}
    F_{ij}^{TD} = A_{D} \vetor{v}_{TD}
    = A_{D}\,\underbrace{C_{0} \frac{\nu_{c}^{t}}{\sigma_{\alpha}}\tens{I}}_{\tens{D}_{TD}} \cdot 
    \left[
        \nabla \ln(\alpha_{d}) - \nabla \ln(\alpha_{c})
        \right]
 \end{equation}
 The closure relation by Burns~\citelater{burns} uses the Favre averaging of the drag
 force and can be expressed as
 \begin{equation}
    F_{ij}^{TD} = C_{D} C_{TD} \frac{\mu_{l}^{t}}{\rho_{c} \sigma_{TD}}\vetor{v}_{TD},
 \end{equation}
 where $C_{D}$ is the drag coefficient, $C_{TD}$ is an adjustable turbulent dispersion
 calibration coefficient, $\mu_{l}^{t}$ is the liquid turbulent viscosity, and
 $\sigma_{TD}$ is the turbulent Prandtl number.

Most lift
 coefficient correlations don't account for the decrease of the magnitude of the
 lift force to zero 
 near the walls. This low gas volume fraction at the walls has historically
 been explained
 through a liquid film forming at the walls repelling the bubbles. This has been demonstrated to
 not actually occur in practice. The wall lubrication force has thus been criticised
 as lacking any physical justification.~\cite{sugrueRobustMomentumClosure,colomboBenchmarkingCFDModelling}
 Newer closures~\citelater{lubchenko} utilise a turbulent dispersion force based 
 formualtion to maintain the desired gas volume fraction and use the closure instead
 as a correction term to resolve the phase distribution at the boundary lost due to
 the averaging process. Star-CCM+'s implementation of the wall lubrication force
 \begin{equation}
    F_{ij}^{WL} = - C_{WL}(y_{w})\alpha_{s} \rho_{p} 
    \frac{|\vetor{v}_{r} - (\vetor{v}\cdot \vetor{n})\vetor{n}|}{d_{b}} \vetor{n}
 \end{equation}
 can be changed to implement alternative models instead by defining user defined 
 field functions for $C_{WL}$.

Surface tension, although an interfacial force, is implemented using the 
 Continuum Surface Force approach as a volumetric force in the VOF formulation.
 Divided into normal and tangential components and using the mean 
 curvature of the free surface 
 $\kappa = - \nabla \cdot \left(\nabla \alpha_{i}/|\nabla \alpha_{i}|\right)$,
 the volumetric surface tension force is given as 
 \begin{equation}
    \vetor{f}_{\sigma} = \underbrace{-\sigma \nabla \cdot \frac{\nabla \alpha_{i}}{|\nabla \alpha_{i}|} \nabla \alpha_{i}}_{\vetor{f}_{\sigma,n}}
     + \underbrace{(\nabla \sigma)_{t}|\nabla \alpha_{i}|}_{\vetor{f}_{\sigma,t}}
 \end{equation}
 The EMP treats surface tension by splitting it among the phases occupying
 the cell using the local volume fractions. The pressure gradient
 is then the summation of the 
 individual phase surface tension contributions $\vetor{f}_{\sigma, i}$,~\cite{gadaLargeScaleInterface2017} ~\citelater{starccm},
 \begin{equation}
    \vetor{f}_{\sigma, i} = \alpha_{i} \sigma \kappa \nabla \alpha_{i}.
 \end{equation}

\subsection{Closures: Under Construction}
\begin{itemize}
    \item Interphase mass transfer (evaporation/condensation)
     Represents phase change, modeled as interfacial flux determined
by local thermodynamic properties (temperature, concentration, pressure—often
using kinetic models for flash evaporation).
    \item Interphase energy transfer
     Encompasses latent heat and sensible heat exchange at the interface 
and throughout the phases (essential for accurate phase change modeling).
    \item Nucleation (wall and bulk)
    \item Interfacial area changes due to bubble growth, coalescence, breakup
    \item Local pressure and temperature gradients driving simultaneous mass and energy transfer
\end{itemize}

\subsection{Numerical Methods}
\COMMENT{------------SOMEWHAT UNDER CONSTRUCTION--------------------}\hfill\\
Star-CCM+ is a commerical CFD software currently maintained and developed 
 by Siemens Digital Industries Software. The software uses the Finite Volume Method to
 discretise the integral form of the governing differential equations over a number 
 of control volumes in the domain. The software has an automatic meshing system but allows
 the implementation of custom meshing using surface wrappers. The relevant variables are
 calculated at the center of each control volume and interpolated to the control volume surfaces.
 Convective and diffusive fluxes are interpolated using the second-order upwind differentiation
 scheme which uses the linear interpolation between two upwind centroids to approximate
 the fluxes at the surfaces of the control volume. Gradients are interpolated using 
 the least squares method with Venkatakrishnan gradient limiters.
 While the VOF formulation uses HRIC, 
 the EMP framework convects volume using either the first- or second-order upwind differentiation.
 In case the Large Scale Interface Detection model is active, 
 HRIC or a scheme that blends HRIC with the first- or second-order 
 upwind scheme can be implemented can also be chosen for volume fraction convection.
 The semi-implicit method for pressure-linked equations (SIMPLE) algorithm is used 
 as the default segregated pressure-velocity coupling scheme. 
\subsection{Workflow?}
\COMMENT{------------UNDER CONSTRUCTION--------------------}