\section{Subproblem: Liquid Infiltration}
The first subproblem deals with water infiltrating the evaporation chamber during rocket ascent. 
The injection system assembly in the experiment consists of: 
\begin{itemize}
    \item the hydraulic accumulator, consisting of two 
    volumes separated by a diaphragm and occupied by 
    low-pressure nitrogen and water respectively.
    \item a pivoted armature valve enabling the flow of water from the 
    accumulator into the cross manifold
    \item the cross manifold to distribute incoming fluid flow
    \item the check valves which finally allow the fluid to flow into the 
    evaporation chamber.
\end{itemize}

The hydraulic accumulator is pressurised to 3.4+/-0.05 bar and heated in order to maintain the temperature of the water contained at 328K.
 During the ascent of the rocket, a pressure relief valve reduces the pressure 
 in the evaporation chamber to $0.03\,\text{MPa}$. Water infiltrates the evaporation chamber shortly before the apogee 
 is reached and the flow is cut off when the internal pressure rises to $0.05\,\text{MPa}$.

The objective of the first task is to model the water injection into the evaporation chamber and extract quantities of interest in order 
 to better estimate the initial conditions for the second task. The multiphase physics models provided by Star-CCM+ are also evaluated and validated
 against the one-dimensional Stefan problem and the two-dimensional Rayleigh-Taylor instability.  
  
 
 
\subsection{Introduction} 
 The evaporation chamber, although a three-dimensional object in real life,
 due to its axial symmetry is modelled as a two-dimensional rectangular domain in Star-CCM+. 


As no flow measurements are made in the injection assembly, and the hydraulic accumulator only contains a temperature sensor, it becomes 
necessary to make assumptions about the flow of the water to the evaporation chamber. 
The reduction adapter reduces the diameter of the outflow pipe from the accumulator, $D$, to the diamter of the rest of pipes used in the 
rest of the injection system, $d$. This is followed by two threaded connections in the form of brass T-joints leading to the cross manifold.
Using the Darcy-Weisbach equation to estimate the head loss through the pipe and estimating the minor head losses in the form of diameter contractions
and threaded connections, the total head loss from the accumulator through to the cross manifold can be written as,
\begin{equation}
    h_{A} = (1 - \frac{d^{2}}{D^{2}})\frac{v_{A}}{2} + 2 (0.08 ) \frac{v_{A}^{2}}{2} + f_{A} \frac{L_{A}}{d} \rho \frac{v_{A}^{2}}{2}
\end{equation}
The water is distributed through the cross manifold into the brass elbows and through to the evaporation chamber. Similar to the above procedure,
the head loss from the manifold to the water outlet incorporates the smooth right angled bends in the elbows and the threaded connections.
Thus,
\begin{equation}
    h_{B} = 2(0.3)\frac{v_{B}^{2}}{2} +  2 (0.08) \frac{v_{B}^{2}}{2} + f_{B} \frac{L_{B}}{d} \rho \frac{v_{B}^{2}}{2}
\end{equation}
As the pipes used in the injection assembly are congruent, the flow is assumed to be distributed uniformly by the cross manifold.
The average velocitiey of water in the first part, $v_{A}$ can thus be related to the outlet velocity, $v_{B}$ using the average flow rates $Q_{A}$
 and $Q_{A}$ respectively.
 \begin{equation}
    v_{A} = \frac{Q_{A}}{A_{A}} = 3 \frac{Q_{B}}{A_{A}} = 3 v_{B} \frac{A_{B}}{A_{A}}
\end{equation}
The energy balance for the system is thus written as 
\begin{equation}
    \frac{\Delta P}{\rho g} = \Delta h + \frac{v_{B}}{2} + h_{A} + h_{B}
\end{equation}
where after using equations and estimating the Darcy friction factor using the Haaland approximation to the Colebrook equation, 
the velocity, $v_{B}$. With a corresponding Reynolds number, $Re = $, the initial assumption of turbulent flow is validated.

With an initial pressure of $0.03MPa$ in the evaporation chamber, it is also necessary to validate if the continuum hypothesis remains valid 
for the air present in the chamber. The Knudsen number relates the mean free path, $\lambda$, to the scale length of the macroscopic flow property gradients 
and helps determine the validity of the continuum hypothesis. The magnitude of the mean free path can be used to estimate the Knudsen number.
\begin{equation}
    \lambda = \frac{\mu}{\rho} \sqrt{\frac{\pi m}{2 k_{B} T}}
\end{equation}
For dry air, at a pressure and temperature of $0.03MPa$ and $328$ respectively, molecular mass $m = 4.815e-26\,\text{kg}$, and estimating the kinematic
viscosity using  Sutherland's formula, the mean free path, $\lambda \approx 2.0732e-06 m$.

\begin{itemize}
    \item Constant density assumption valid? Does that break the rayleigh taylor benchmark test?
    \item CHANGE INLET FLOW TO ACCOUNT FOR CONSTANCY OF NONDIM NUMBERS
\end{itemize}
%\subsubsection{Physical Background}
\subsection{Problem Description}



\subsection{Validation Problems}
\subsubsection{Stefan Problem}
Phase changes can be regarded as the growth of the domain of one phase accompanied by the reduction of the domain of the other phase. 
This growth or reduction in domain sizes can be triggered by thermal as well as non-thermal processes~\citelater{shumon koga} 
and the representative mathematical dynamic model containing moving boundaries is known as the Stefan system. The associated problem of 
analysing and finding the solutions to the aforementioned model is known as the Stefan problem.~\citelater{koga}. 
The classical Stefan problem is a one dimensional solidification or melting problem~citelater{jonas, jonsson}. The one-dimensional 
Stefan problem under semi-infinite geometry, uniform initial temperature, constant boundary temperature, and 
thermophysical properties constant in each phase is probably the simplest, explicitly solvable problem of phase 
change~\citelater{lectures, uni tenessee knoxville lectures}, serving as a good benchmark to validate the phase change VOF solver in Star-CCM+.
~\COMMENT{DOES IT ALSO SERVE AS A GOOD BENCHMARK FOR SIMPLE HEAT CONDUCTION TOO??? BECOZ TWO BIRDS ONE STONE}

Assuming that the region in space, $\Omega \subset \mathbb{R}^{2}$, occupied by the material is the 2D semi-infinite rectangle 
$\Omega = \{(x,y) \in \mathbb{R} \cross \mathbb{R}:\,x \in [0, \infty),\,y \in [0, \Delta h]\}$, with the solid phase and the liquid phase 
occupying the regions $\Omega_{s}$ and $\Omega_{l}$ respectively such that $\Omega = \Omega_{s} \cup \Omega_{l}$. At any given time, $t$, the 
two phases are separated by the interface, $\Gamma(t)$, that marks the change in phase of the material. The boundary of the domain $\Omega$ is 
denoted by $\partial \Omega$.
The problem space, $\mathcal{D}$, is the spatial and temporal domain occupied by the material, $\mathcal{D} = \{[t_{0}, t_{f}] \cross \Omega\}$. 
With the heat equation governing the temperature field in the liquid region, the Stefan condition at the interface, and the respective boundary 
conditions, the system of equations defining the one-dimensional Stefan problem can be written as,
\begin{align}\label{stef: eqn_system}
    \begin{split}
    \begin{cases}
        \frac{\partial T}{\partial t} - \alpha \frac{\partial^{2} T}{\partial x^{2}}& = 0,\\
        \rho h_{m} \frac{d \Gamma(x(t), t)}{d t} + \kappa \frac{\partial \Gamma(x(t), t)}{\partial x}& = 0,\\
        T(x, 0)& = T_{l},\\
        \nabla T(x, t) \cdot \mathbf{n}& = 0,\\
        T(x, 0)& = T_{m}
    \end{cases}
\end{split}
\end{align}   
- the system of equations is well-posed and has a unique solution. the evolution of the temperature field along with the evolution of the 
phase change interface is studied.
The simulation assumes laminar and unsteady flow and solves for the solution variables implicitly using the SIMPLE scheme.
 The 2D region is discretised using a uniform orthogonal quadrilateral mesh of varying sizes in order to 
 study the spatial convergence of the solution. The physical parameters for the simulation are selected according to water ice, as in~\citelater{boledi et al}.
 A constant density $\rho = 1000\,\text{kg}\cdot\text{m}^{-3}$, dynamic viscosity
 $\mu = 8.8871e-4\,\text{Pa}\cdot\text{s}$, latent heat of fusion $100000 \,\text{J}\cdot\text{kg}^{-1}$, and 
 specific heat $4200\,\text{J}\cdot\text{kg}^{-1}\text{K}^{-1}$. Thermal conductivities are defined as $2.33\,\text{W}\cdot\text{m}^{-1}\text{K}^{-1}$ 
 and $0.62\,\text{W}\cdot\text{m}^{-1}\text{K}^{-1}$ for the liquid and solid phases respectively. 
 All four boundaries are assigned a no-slip shear stress specification. The boundary at $x = 0$ is assigned a constant temperature, $T =273\,\text{K}$, 
 while the other boundaries are assumed to be adiabatic. 
 The convection and diffusion
 terms are discretised using the second-order upwind scheme and the least squares method was used to interpolate the values of the 
 gradients from the cell centres onto the face centres. The transient term is discretised using the implicit Euler-method which is first-order accurate.
 First-order HRIC is used to reconstruct the interface. Since Star-CCM+ sets under- and over-relaxation factors conservatively, the values are left unchanged.

The evolution of the temperature field for the simulation with cell size, $\Delta h = 5e-3$ is shown in Figure~\COMMENT{FIG}. A clear propagation of
 the interface from the left to right is observed with increasing simulation times. The temperature also gradually decreases in the liquid phase from the Dirichlet
 boundary at $x = 0$ towards the melting temperature, $T_{m}$, at the interface after which it stays constant. 

\begin{itemize}
    \item 'This is exactly what one would expect for a velocity that is decreasing in time as is the case for the classical Stefan problem. 
One can also see that all simulation results converge to the analytical solution for a finer mesh and a smaller time step.'
    \item \COMMENT{ABOUT CONVERGENCE}
    \item \COMMENT{ABOUT COMPARISON OF TEMPERATURE W ANALYTICAL SOLUTION}
    \item \COMMENT{ABOUT COMPARISON OF PCI W ANALYTICAL SOLUTION}
\end{itemize}

\subsubsection{Rayleigh-Taylor Instability}
When two superposed fluids with differing densities are accelerated in a direction perpendicular to their interface, the surface 
is unstable when the heavier fluid is accelerated into the lighter fluid.~\citelater{ref 15, p192 - Birkhoff, 1954}. The instability 
arising therefrom is known as the Rayleigh-Taylor (RT) instability. 
The growth of perturbations at the interface is characterised by opposing pressure and density 
gradients~\citelater{Banerjee 2020, Schilling et all 2020, HutchinsonDissertation} and the density difference is represented by 
the \textit{Atwood number}, $At = (\rho_{H} - \rho_{L})/(\rho_{H} + \rho_{L}).$
Although not encountered in its ideal form, the RT instability may occur across various natural and technological processes where it 
is often modified by the presence of additional processes~\COMMENT{mention which processes?}. The principles governing the nonlinear 
RT instability also govern any motion of one fluid in another of different density~\citelater{Tryggvason rt instability}, thus 
serving as a good measure to study the infiltration of the evaporation chamber in the first 
subproblem. 
The instability has moreover served as a classical benchmark for the evaluation of the behaviour of two phase 
flows~\citelater{Goulding et al.}~\COMMENT{'WHY' imminent}.

We assume that the two immiscible, viscuous, and incompressible fluids occupy the regions,
\begin{equation*}
    \Omega_{i}(t) = \{(x,y) \in \mathbb{R} \cross \mathbb{R}: (-1)^{i}(y - h(t,x)) > 0,\,t \geq 0\}, \,\, i = 1,2
\end{equation*}
and are separated by the interface, $\Gamma(t)$ where
\begin{equation*}
    \Gamma(t) = \{(x,y) \in \mathbb{R} \cross \mathbb{R}: y = h(t,x),\, t \geq 0 \}
\end{equation*}
Using the navier stokes equations for incompressible fluids, a mixture density and viscosisty, the jump conditions at the interfaces, and the 
initial boundary conditions, the governing equation for the Rayleigh-Taylor instability can be written as
\begin{align}\label{rt: eqn_system}
    \begin{split}
    \begin{cases}
        \rho \frac{\partial (\mathbf{u})}{\partial t} + \rho \nabla \cdot (\mathbf{u} \mathbf{u})& = -\nabla p + \mu \nabla^{2} \mathbf{u} + \mathbf{g}\rho,\\
        \nabla \cdot \mathbf{u}& = 0,\\
        [\![S(u, p + \mathbf{g}\rho)\mathbf{n}]\!] &= \sigma \kappa \mathbf{n} + [\![\rho]\!] \mathbf{g} y\\
        [\![u]\!] &= 0\\
        V &= \mathbf{u} \cdot \mathbf{n}\\
        u(0) &= u_{0},\\
        \Gamma(0) &= \Gamma_{0}
    \end{cases}
\end{split}
\end{align}   
where $\rho$ is the density, $\mathbf{u}$ is the velocity vector, $p$ is the pressure, $\mu$ is the dynamic viscosity, and $g$ is the gravitational acceleration.

In a system of two fluids with a perturbed interface, the heavier fluid penetrates the lighter fluid due to gravitation thereby pushing the lighter fluid upwards.
 The initial perturbations, generally studied using linear stability analysis, lead to an exponential growth~\citelater{andrews and dalziel} and transition into
 non-lineartiy resulting in the rise and sink of the bubbles of lighter fluid and spikes of the heavier fluid respectively~\citelater{sharp, bannerjee}. 
 Figure~\COMMENT{name figure} illustrates the parameter definitions and nomenclature of an evolving single-mode~\COMMENT{need i define single mode rt?} RT 
 instability interface.

The simulation assumer turbulent and unsteady flow, utilising the SIMPLE implicit scheme. The computational domain is discretised using an orthogonal quadrilateral mesh.
 The convection and diffusion terms are discretised using the second-order upwind scheme while the least squares method is again used to interpolate the values
 of the gradients from the cell centres onto the face centres. The VOF solver utilises the first-order HRIC scheme to reconstruct the interface.
 The transient term is discretised using the first-order accurate implicit Euler-method. The modified K-Omega (SST k-omega) model is used to account for turbulence and surface
 is treated semi-implicitly.~\COMMENT{MENTION INITIAL CONDITIONS}
The instability is simulated on a 2D rectangular domain, $[0, L_{x}] \cross [0, 4L_{x}]$, where $L_{x}$ is the reference length. 
 The initial interface, located at $y_{0}$, represents a single-mode perturbation with amplitude, $A = 0.1 L_{x}$, and 
 wavelength, $\lambda = L_{x}$.
        \begin{equation*}
           \Gamma_{0} = 2 L_{x}+ A \cos(\frac{2\pi}{ L_{x} })
        \end{equation*}
       
The lower limit of the high Atwood number regime requires the Atwood number to be atleast $0.5$~\cite{HutchinsonDISSERTATIONSUBMITTEDFACULTY}. 
Gravitational acceleration acts in a downward direction with a magnitude of $g = 1.0$. Periodic boundary conditions are enforced in the 
horizontal direction and slip wall conditions are applied at the top and bottom boundaries. The physical parameters are selected to make 
the simulations dynamically similar to the ones studied in~\cite{hamzehlooDirectNumericalSimulations2021}.
        
According to~\cite{MIRJALILI2019221}, a reasonable solution to the RT instability with $At \approx 0.75$ can be obtained with 
a $128 \cross 512$ mesh. With similar mesh resolutions being used in~\cite{hamzehlooDirectNumericalSimulations2021, 
HuangConsistentEssentiallyConservative2020} to study similar RT instabilities, in addition to a mesh convergence study being performed, 
the domain is discretised using a uniform orthogonal quadrilateral mesh with size $\delta_{h} = 0.0045$. The timestep for the simulations is 
selected as $\delta t = 2.5 \cross 10e-4/\sqrt{At}$ similar to~\cite{DingDiffuseInterfaceModel2007,hamzehlooDirectNumericalSimulations2021}. 
The following cases are studied:\\
\begin{tabularx}{0.8 \textwidth}{ >{\centering\arraybackslash}X >{\centering\arraybackslash}X  >{\centering\arraybackslash}X  >{\centering\arraybackslash}X >{\centering\arraybackslash}X}
    \hline
    Case & $At$ & $Re$ & $\sigma$ & $\delta_{h}$\\
    \hline
    1 & $0.5$ & $300$ & $1e-5$ & $0.05$\\
    2 & $0.5$ & $300$ & $1e-5$ & $0.007$\\
    3 & $0.5$ & $300$ & $1e-5$ & $0.0045$\\
    4 & $0.5$ & $300$ & $1e-5$ & $0.0025$\\
    5 & $0.2$ & $1000$ & $1e-5$ & $0.0045$\\
    6 & $0.5$ & $1000$ & $1e-5$ & $0.0045$\\
    5 & $0.5$ & $3000$ & $1e-5$ & $0.0045$\\
    6 & $0.5$ & $3000$ & $1e-5$ & $0.0045$\\
    \hline
\end{tabularx}
\newline
In a system of two fluids with a perturbed interface, the heavier fluid penetrates the lighter fluid due to gravitation thereby pushing the lighter fluid upwards. The initial perturbations, generally studied using linear stability analysis, lead to an exponential growth~\citelater{andrews and dalziel} and transition into non-lineartiy resulting in the rise and sink of the bubbles of lighter fluid and spikes of the heavier fluid respectively~\citelater{sharp, bannerjee}. Figure~\ref{rt_definitions} illustrates the parameter definitions and nomenclature of an evolving single-mode~\COMMENT{need i define single mode rt?} RT instability interface. The evolution of RT instabilities for Reynolds numbers 300, 1000, and 3000 are depicted in figure~\ref{rt_reynolds}. As the solution evolves, the penetration of the spike increases and it eventually rolls up and forms two transient counter-rotating vortices due to shear forces and Kelvin-Helmholtz type instabilities~\citelater{hamzelhoo}, which go on to contribute to turbulent mixing and chaotic flow features~\citelater{Sharp}.

Figure~\COMMENT{name figure} depicts the evolution of the interface at different times for varying density ratios as simulated in Star-CCM+. Upto high Reynolds numbers, the interface structure and its temporal evolution agree qualitatively with the results published in~\citelater{hamzelhoom huang, ding}.~\COMMENT{why does it look different at high Re}.
Using the bubble and spike heights, defined as the maximum vertical distance of the spike and bubble as measured from the undisturbed initial interface, the results can be quantitatively compared to~\citelater{hamzelhoo} as shown in Figure~\ref{rt_heights}. Table~\ref{table_rt_errs} summarises the root mean square errors and the maximum errors between the simulated results and~\citelater{hamzelhoo}.

Simulations conducted for Atwood numbers very close to one also qualitatively show a similar progression and evolution of structures as the simulations in~\citelater{huang}.~\COMMENT{What happens at high atwood numbers}

~\COMMENT{Write about mesh convergence study. WHY DO RESULTS NOT MATCH?}.
\begin{itemize}
    \item \COMMENT{ABOUT SPATIAL AND TEMPORAL CONVERGENCE}
    \item \COMMENT{ABOUT EVOLUTION OF INTERFACE W VARYING REYNOLDS AND VARYING ATWOOD: } Figure~\COMMENT{FIGFIG} and 
    figure~\COMMENT{GIFGIF} depict the evolution of the interface at different times for varying density ratios and Reynolds numbers 
    respectively  as simulated in Star-CCM+. Upto high Reynolds numbers, the temporal evolution and the structural features of the 
    interface agree qualitatively with the results  published in~\citelater{hamzelhoom huang, ding}. As the solution evolves, 
    the penetration of the spike increases and it eventually rolls up and forms two transient counter-rotating vortices due to 
    shear forces and Kelvin-Helmholtz type instabilities~\citelater{hamzelhoo}, which go on to contribute to turbulent mixing and 
    chaotic flow features~\citelater{Sharp}.~\COMMENT{WHY DO HIGH Re NUM SIMS DEVIATE FROM EXPECTED. MENTION SALIENT FEATURES OF THE EVOLUTION} 
    Simulations conducted for Atwood numbers very close to one also qualitatively show a 
    similar progression  and evolution of structures as the simulations in~\citelater{huang}.~\COMMENT{What happens at high atwood 
    numbers}
    \item~\COMMENT{ABOUT COMPARISON OF BUBBLE HEIGHTS W DNS DATA AND L2 AND L-INF ERRORS: }  Using the bubble and spike heights, defined as the maximum vertical distance of the spike and bubble as measured from the undisturbed initial interface,
 the results can be quantitatively compared to~\citelater{hamzelhoo} as shown in Figure~\ref{rt_heights}. Table~\ref{table_rt_errs} summarises the root 
 mean square errors and the maximum errors between the simulated results and~\citelater{hamzelhoo}.
\end{itemize}

\subsubsection{Liquid Infiltration of Evaporation Chamber}
\begin{itemize}
    \item \COMMENT{ABOUT CONVERGENCE}
    \item \COMMENT{ON EVOLUTION OF INTERFACE and FLOW FIELD and RESULTING HEIGHT OF WATER}
    \item \COMMENT{ON EVOLUTION OF TEMPERATURE FIELD}
\end{itemize}

\subsection{Conclusion?}

%\subsection{Numerical Analysis}
%\subsubsection{Stefan Problem}
%\begin{itemize}
%    \item \textbf{Convergence}
%    \item \textbf{Results}
%    \item \textbf{Errors}
%\end{itemize}%

%\subsubsection{Rayleigh-Taylor Instability}
%\begin{itemize}
%    \item \textbf{Convergence}
%    \item \textbf{Results}
%    \item \textbf{Errors}
%\end{itemize}

%\subsubsection{Actual Problem}
